---
title: "R Markdown for Politics and Policy: <br>From Data to Manuscript"
output: github_document
---

### [Policy & Politics Workshop](https://poli-sci.utah.edu/)

---

```{r child = here::here('content/schedule/index.md')}
```

---

## Overview

In this full-day workshop, you'll learn how to get more out of R Markdown (and friends). We will demystify how R Markdown works under the hood. You will learn practical tools and workflows to increase your efficiency and productivity using R Markdown (including RStudio IDE features and templates), while learning how to use some extension packages along the way. We assume that you have knit an R Markdown document before, but you don’t need to be an advanced R Markdown user to take this workshop. 

## Instructor

Ian Adams is a Ph.D. candidate in Political Science at the University of Utah, where he also completed a Masters of Public Administration. His research interests include body-worn cameras and policing. Ian is a 2018 American Society of Public Administration Founders' Fellow, and a 2020/2021 doctoral fellow of the Academy of Criminal Justice Sciences. Personal website (and current CV) available at www.ianadamsresearch.com. He lives in Salt Lake City with his partner, four kids, two dogs, and one bird.

## Pre-work

```{r child = here::here('content/materials/prework/index.Rmd')}
```

---

[![forthebadge](https://forthebadge.com/images/badges/cc-by.svg)](https://creativecommons.org/licenses/by/4.0/)  
This work is licensed under a [Creative Commons Attribution 4.0
International License](https://creativecommons.org/licenses/by/4.0/).
